Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-10-28 manuscript.tex
20161028

Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. Aslanov et al. presented a thruster method driving the space tethered tug, and analyzed the dragging dynamics~\cite{aslanov2013dynamics}. Huang et al. investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}. This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par

@@

Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as:

@@

Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function:

@@

and utilize Lagrangian mechanics theory to obtain the following expression

@@

Before declaring the controller design, some basic precondition is prepared for proceeding derivation.  The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions. $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form. Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$:

@@

\textcolor{red}{So far, the proposed control laws have been verified in the undisturbed environment. However, space perturbations and parameter uncertainties usually occur during the deployment of the tethered satellite system in engineering application. For checking the robustness of the proposed control laws, based on the dynamics~(\ref{eq:dynamics 1}), we have the following assumptions about uncertainties and disturbances:

@@

x/\nu,&\vert x\vert <\nu\\

@@

The simulation results of the deployment dynamics subjected to uncertainties are shown from Fig~\ref{fig:7} to Fig~\ref{fig:10}. In Fig~\ref{fig:7}, although there exist the parameter uncertainties, QST-SMC still performs the best deployment among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}. In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique. Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to uncertainties and disturbances.}

>>>>

Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}. Huang et al. investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}. This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par

@@

Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:

@@

Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function~\cite{Mantellato2015}:

@@

and utilize Lagrangian mechanics theory to obtain the following expression\cite{Sun2014304,Mantellato2015}

@@

Before declaring the controller design, some basic precondition is prepared for proceeding derivation.  The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions. $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form. Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$~\cite{parra2003dynamic}:

@@

\textcolor{red}{So far, the proposed control laws have been verified in the undisturbed environment. However, space perturbations and parametric uncertainties usually occur during the deployment of the tethered satellite system in engineering application. For checking the robustness of the proposed control laws, based on the dynamics~(\ref{eq:dynamics 1}), we have the following assumptions about uncertainties and disturbances:

@@

x,&\vert x\vert <\nu\\

@@

The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}. In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}. In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique. Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to uncertainties and disturbances.}
